### 2025-03-09 download-football-data.qmd
20250308 - citations
20250308 - reorder archive link

@@

- <https://nflreadr.nflverse.com/articles/dictionary_pfr_passing.html> [@HoPFRPassing]
- <https://www.pro-football-reference.com/about/advanced_stats.htm> [archived at <https://perma.cc/LKH5-92PQ>; @PFR2025]

>>>>

We use the `nfl4th` package [@R-nfl4th] to download fourth down data.

@@

- <https://nflreadr.nflverse.com/articles/dictionary_pfr_passing.html> [@HoPFRPassing]
- <https://www.pro-football-reference.com/about/advanced_stats.htm> [@PFR2025; archived at <https://perma.cc/LKH5-92PQ>]

### 2025-03-09 fantasy-football.qmd
20250308 - reorder archive link

Fantasy football is one of the most widely played games in the history of games.
It is estimated that around 62 million people play fantasy sports [archived at <https://perma.cc/9PB8-ZDJJ>; @FSGA2023], of whom around 29 million play fantasy football [archived at <https://perma.cc/8YSN-UUNT>; @statistica2023a].
As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available for [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.

>>>>

Fantasy football is one of the most widely played games in the history of games.
It is estimated that around 62 million people play fantasy sports [@FSGA2023; archived at <https://perma.cc/9PB8-ZDJJ>], of whom around 29 million play fantasy football [@statistica2023a; archived at <https://perma.cc/8YSN-UUNT>].
As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available for [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.

### 2025-03-09 index.qmd
20250308 - reorder archive link

I strive to follow [principles of accessibility](https://bookdown.org/yihui/rmarkdown-cookbook/html-accessibility.html) [archived at <https://perma.cc/8XJ9-Q6QJ>; @Xie2024; @Xie2020_packages] to make the book content accessible to people with visual impairments and physical disabilities.
If there are additional ways I can make the content more accessible, please let me know.

>>>>

I strive to follow [principles of accessibility](https://bookdown.org/yihui/rmarkdown-cookbook/html-accessibility.html) [@Xie2024; @Xie2020_packages; archived at <https://perma.cc/8XJ9-Q6QJ>] to make the book content accessible to people with visual impairments and physical disabilities.
If there are additional ways I can make the content more accessible, please let me know.
